\documentclass[10pt,xcolor=svgnames,fleqn,aspectratio=169]{beamer}

\usepackage{tikz}
\usepackage{hyperref}
\usepackage{xcolor,colortbl}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\usepackage{cancel}
\usepackage[T1]{fontenc}

\def\blue{\color{DodgerBlue}}
\def\green{\color{Green}}
\def\red{\color{Red}}
\def\Orchid{\color{Orchid}}
\definecolor{DodgerBlueDark}{HTML}{1873cc}

\mode<presentation>
\usetheme{Copenhagen}
\usecolortheme[named=DodgerBlueDark]{structure}
%\useoutertheme{infolines}
\useoutertheme[footline=authortitle]{miniframes}
%\setbeamertemplate{headline}[infolines theme]
\setbeamertemplate{headline}[default]
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[miniframes theme]
\setbeamertemplate{footline}[page number]
\setbeamertemplate{itemize items}[default]
\setbeamertemplate{enumerate items}[default]

\newcommand{\dr}{$\Delta R$~}
\newcommand{\dm}{$\Delta m$~}
\newcommand{\dphi}{$\Delta \phi$~}
\newcommand{\pt}{$p_{T}$~}
\newcommand{\texeta}{$\eta$~}
\newcommand{\nj}{$N_\mathrm{jets}$~}
\newcommand{\met}{$\cancel{E}_{T}$~}
\newcommand{\lowdm}{low~$\Delta m$~}
\newcommand{\highdm}{high~$\Delta m$~}
\newcommand{\bug}{\textbf{Bug}}
\newcommand{\fix}{\textbf{Fix}}

\title{Z to Invisible: Data and MC Stack Plots}

\author{\textcolor{DodgerBlueDark}{\bf C.~Smith\inst{1}}}
\institute{\inst{1} Baylor University}
\date{\today}

\renewcommand{\arraystretch}{1.2}
\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}{Overview}
Data vs MC in Lepton and Photon CRs
\begin{itemize}
\item Low \dm and High \dm selections
\item Medium IDs used for electrons, muons, and photons.
\item For Nb, mtb, and ptb
\begin{itemize}
\item Jet $p_T > 20$ GeV requirement (constant)
\end{itemize}
\item For JetID and HEMVeto
\begin{itemize}
\item Jet $p_T > 30$ GeV requirement (constant)
\end{itemize}
\item For the Resolved TopTagger
\begin{itemize}
\item Jet $p_T > 40, 30, 20$ GeV for the three input jets (constant)
\end{itemize}
\item nJets, dPhi, HT, sMET
\begin{itemize}
\item Jet $p_T > 20, 30$ GeV requirements (tried each cut separately)
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Bug Fixes}
\begin{enumerate}
\item \bug: The saved histograms had variables calculated with only jet $p_{T} > 20$ GeV.
\begin{itemize}
\item \fix: Save histograms with variables calculated with different jet \pt cuts.
\end{itemize}
\item \bug: To clean the AK8 jet collection, we were using Electron\_jetIdx, Muon\_jetIdx, and Photon\_jetIdx to match to AK8 jets, but these variables only match to AK4 jets.
\begin{itemize}
\item \fix: Only use \dr matching to clean AK8 jets.
\end{itemize}
\item \bug: When running the top tagger, we were using Jet\_matchesElectron, Jet\_matchesMuon, and Jet\_matchesPhoton to filter AK8 jets.
\begin{itemize}
\item \fix: Use FatJet\_matchesElectron, FatJet\_matchesMuon, and FatJet\_matchesPhoton.
\end{itemize}
\item \bug: To select the ISR jet, we were only using the 2016 working point for the b--tag discriminator cut to check if the AK8 subjets were b--jets.
\begin{itemize}
\item \fix: Use b--tag working points from 2016, 2017, and 2018 for each year respectively.
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}{Selection Changes}
\begin{itemize}
\item Consistently use one photon passing ID for jet cleaning, modified MET, and selection.
\item Use different jet $p_T > 20, 30$ GeV cuts for Z to NuNu MC which can be used for the background prediction.
\item Use a ``tight \lowdm'' selection
\begin{itemize}
\item ISR jet $p_{T} > 300$ GeV
\item $\cancel{E}_{T} > 300$ GeV
\item Did not require exact matching to SR (low\_dm\_SB\_index != -1) as this requires further implementation.
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Conclusions}
Photon CR: \lowdm vs. tight \lowdm
\begin{itemize}
\item Tight \lowdm  selection removes approx. 30\% more Data and MC events compared to \lowdm selection.
\item Tight \lowdm does not show a significant improvement in Data vs. MC agreement compared to \lowdm.
\end{itemize}
Photon CR: jet $p_{T} > 20$ GeV vs. jet $p_{T} > 30$ GeV
\begin{itemize}
\item The jet $p_{T} > 30$ GeV selection removes approx. 18\%, 58\% (\lowdm, \highdm) more Data vs. MC events compared to the jet $p_{T} > 20$ GeV selection.
\item The jet $p_{T} > 30$ GeV selection results in improved Data vs. MC agreement (mainly in 2017 and 2018) compared to the jet $p_{T} > 20$ GeV selection.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{stack_snippet.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}